RE: Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-03-09 rmd/figures.Rmd
edit: figure caption
edit: manuscript

---
title: "Figures"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE)
```

```{r figure1, fig.width=12, fig.height=6}
source(here::here("code/figure_concept.R"))
print(g_concept)
```

**Figure 1** (A) Example of simulated branching networks. Node color is reflective of the disturbance value calculated in network generation. (B) Distribution of disturbance values in branching networks. (C) Trophic interactions in a three-species community. $B$ refers to a basal species whose population level is controlled by a density-dependent function. The consumer species (or intraguild prey), $C$, consumes $B$ as a resource. The predator (or intraguild predator), $P$, is able to consume both $B$ and $C$. The structure and strength of these trophic interactions determined by functional responses. The strength of trophic interactions involving $P$ is represented by the darkness of the arrows (strength of the $B$-$C$ interaction is fixed), and food chain length varies in response to the proportion that each resource makes to the diet of $P$. On the far left, a simple linear food chain exists when the predator does not consume the basal species. Moving to the right, basal species' biomass is converted to predator biomass at higher efficiencies with greater attack rates. (D) Preference of predator $P$ to basal species $B$ over consumer $C$ under different omnivory scenarios. The preference changes with the relative density of $B$ to $C$ ($C=50$ in this example), and the rate of change is determined by attack rate and handling time.

@@

```{r figure2, fig.width=12, fig.height=5.5}
source(here::here("code/figure_main_sim.R"))
print(g_ld)
```

**Figure 2** Ecosystem size (A) and complexity (B) have little influence on food chain length under low disturbance regime. Lines are loess curves fitted to simulated data and are colored based on omnivory. Shaded ribbons are 95% confidence intervals. Parameters for low disturbance regime: disturbance probability $p_d = 0.01$ and mean proportional mortality at headwaters $\mu_{m}=0.8$.

@@

```{r figure3, fig.width=12, fig.height=5.5}
source(here::here("code/figure_main_sim.R"))
print(g_hd)
```

**Figure 3** Ecosystem size (A) and complexity (B) influence food chain length under high disturbance regime. Lines are loess curves fitted to simulated data and are colored based on omnivory. Shaded ribbons are 95% confidence intervals. Parameters for high disturbance regime: disturbance probability $p_{d} = 0.01$ and mean proportional mortality at headwaters $\mu_{m}=0.8$.

>>>>

---
output: pdf_document
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE)

options(knitr.kable.NA = '')
```

# Tables

```{r}
source(here::here("code/table_param.R"))

knitr::kable(df_value %>%
               dplyr::select(-"One-patch") %>% 
               rename(Value = "Main"),
             escape = FALSE,
             booktabs = TRUE,
             caption = "Parameter values used in the main simulation") %>% 
  kableExtra::kable_styling(latex_options = 'HOLD_position')
```

@@

# Figures

```{r figure1, fig.width=12, fig.height=6}
knitr::include_graphics(here::here("figure/figure_concept.pdf"))
```

**Figure 1** (A) Example of simulated branching networks. Node color is reflective of the disturbance value calculated in network generation. (B) Density distributions of disturbance intensity (i.e., proportional reduction of a population). Three networks of 50 patches were produced with varied branching probabilities, which were shown in different colors. The vertical line indicates the mean disturbance intensity at headwaters ($\mu_m = 0.8$). (C) Trophic interactions in a three-species community. $B$ refers to a basal species whose population level is controlled by a density-dependent function. The consumer species (or intraguild prey), $C$, consumes $B$ as a resource. The predator (or intraguild predator), $P$, is able to consume both $B$ and $C$. The structure and strength of these trophic interactions determined by functional responses. On the far left, a simple linear food chain exists when the predator does not consume the basal species. Moving to the right, basal species' biomass is converted to predator biomass at higher efficiencies with greater attack rates. (D) Proportional contribution of basal species $B$ to predator $P$ under different omnivory scenarios. The contribution changes with the relative density of $B$ to $C$ ($C=50$ in this example), and the rate of change is determined by attack rate and handling time.

@@

```{r figure2, fig.width=12, fig.height=5.5}
knitr::include_graphics(here::here("figure/figure_main_n_patch.pdf"))
```

**Figure 2** Relationships between food chain length and ecosystem size with high disturbance intensity $\mu_m = 0.8$. Lines indicate loess curves, and shades are associated 95% confidence intervals. Rows distinguish food web motifs, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities.

```{r figure3, fig.width=12, fig.height=5.5}
knitr::include_graphics(here::here("figure/figure_main_p_branch.pdf"))
```

**Figure 3** Relationships between food chain length and ecosystem complexity with high disturbance intensity $\mu_m = 0.8$. Lines indicate loess curves, and shades are associated 95% confidence intervals. Rows distinguish food web motifs, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities.

### 2023-03-09 rmd/manuscript.Rmd
edit: manuscript

Understanding the drivers of food chain length in natural communities has intrigued ecologists since Elton publicized 'food cycles' in the early 20th century. Proposed drivers of food chain length have included productivity, disturbance regime, ecosystem size, and trophic omnivory. However, current theories have largely assumed simple, two-dimensional habitat architectures and may not be adequate to predict food chain length in ecosystems with a complex, branching structure. Here, we develop a spatially explicit theoretical model which provides an integrated framework for understanding variation in food chain length in branching networks. We show independent, positive influences of ecosystem size and complexity on food chain length. However, these effects were contingent upon other drivers. In particular, the effects of ecosystem size and complexity appeared more clearly in high-disturbance regimes. Our results suggest that ecosystem complexity is an important yet overlooked driver of food chain length in branching ecosystems.

@@

Among the three hypotheses, the ecosystem size hypothesis has been consistently supported in empirical explorations, likely because it encompasses multiple mechanisms [@takimotoEnvironmentalDeterminantsFoodchain2013]. For example, large ecosystems have increased species richness (species-area relationship [@lomolinoEcologyMostGeneral2000]), are buffered against disturbances [@saboRoleDischargeVariation2010], and have greater numbers of immigrant sources in the ecosystem with stable metapopulations [@takimotoEnvironmentalDeterminantsFoodchain2013]. Meanwhile, the productivity and disturbance effects are highly sensitive to the internal structure of food web motifs. As such, the effects of disturbance and resource availability on FCL have been found to be highly variable among ecosystem types and geographic regions [@takimotoEffectsProductivityDisturbance2012; @diehlIntraguildPreySuffer2001; @takimotoEnvironmentalDeterminantsFoodchain2013; @postLongShortFoodchain2002].

@@

Under each motif, we crossed values of disturbance (frequency and intensity), productivity, and dispersal. Disturbance frequency and intensity were controlled via $p_m$ ( `r unique(df_sim$p_disturb) %>% sort()`) and $\mu_m$ (`r unique(df_sim$mean_disturb_source) %>% sort()`), respectively. Spatial disturbance patterns were regulated by variation in disturbance intensity at headwaters ($\sigma_{h}=$ `r max(df_sim$sd_disturb_source)`), and local variation ($\sigma_{l}=$ `r min(df_sim$sd_disturb_lon)`). This setup ($\sigma_h > \sigma_l$) produces high spatial variation among tributaries while allowing strong within-tributary downstream correlation [@teruiEmergentDualScaling2021], a typical pattern in real river networks [@nakamuraDisturbanceRegimesStream2000; @bendaNetworkDynamicsHypothesis2004]. We used a combination of basal species' growth rate $r_b$ and base carrying capacity $K_{base}$ (low productivity: $r_b =$ `r min(df_sim$r_b)`, $K_{base} =$ `r min(df_sim$base_k)` ; high productivity = $r_b =$ `r max(df_sim$r_b)`, $K_{base} =$ `r max(df_sim$base_k)` ) as a proxy for resource availability. For dispersal, we examined short- and long-distance dispersal scenarios (short-distance dispersal $\theta=$ `r max(df_sim$theta)`; long-distance dispersal $\theta=$ `r min(df_sim$theta)`) with constant dispersal probability ($p_{d}=$ `r unique(df_sim$p_dispersal)`).

@@

The most significant finding in this study is the synergistic effects between ecosystem geometry and disturbance. Our no-disturbance scenario can be viewed as habitat networks having nearly homogeneous environments, in which long food chains were generally supported independently of ecosystem size and complexity (except the chain motif with low productivity). However, as the frequency of intense disturbance increases, small and/or simple networks become unable to maintain long food chains. Here, increased ecosystem size and complexity may give greater resistance to disturbance through different mechanisms. Ecosystem size increases the "total amount" of disturbance refugia, from which dispersing propagules recolonize impacted habitat patches. In the meantime, ecosystem complexity may increase the connectivity to disturbance refugia. Branching shortens the mean distance between patches and, therefore, may enhance immigration from less disturbed patches (**Figure S10**). The proportion of disturbance refugia may have increased in more branched networks. However, we did not observe a proportional increase in disturbance refugia with increasing branching probability. Collectively, each of the geometric features likely supports long food chains through distinct mechanisms, which may also explain the different patterns of state transitions (additive vs. insertion mechanisms) [@postProximateStructuralMechanisms2007]. While empirical studies rarely looked at the influence of ecosystem complexity on FCL, several studies provide some support for this theoretical prediction. For example, @sullivanEcosystemStructureEmerges2015 reported FCL is controlled primarily by the number of tributary confluences in Idaho streams. Similarly, it has been shown that the merging of major tributaries lengthened FCL in the Colorado River, especially during a post-monsoon turbid water phase [@saboPulsedFlowsTributary2018]. More empirical research is needed to confirm our theoretical predictions.

>>>>

Understanding the drivers of food chain length in natural communities has intrigued ecologists since Elton publicized 'food cycles' in the early 20th century. Proposed drivers of food chain length have included productivity, disturbance regime, ecosystem size, and trophic omnivory. However, current theories have largely assumed simple, two-dimensional habitat architectures and may not be adequate to predict food chain length in ecosystems with a complex, branching structure. Here, we develop a spatially explicit theoretical model which provides an integrated framework for understanding variation in food chain length in branching networks. We show independent, positive influences of ecosystem size and complexity on food chain length. However, these effects were contingent upon other drivers. In particular, the effects of ecosystem size and complexity appeared more clearly in high-disturbance and high-productivity regimes. Our results suggest that ecosystem complexity is an important yet overlooked driver of food chain length in branching ecosystems.

@@

Among the three hypotheses, the ecosystem size hypothesis has been consistently supported in empirical explorations, likely because it encompasses multiple mechanisms [@takimotoEnvironmentalDeterminantsFoodchain2013]. For example, large ecosystems have increased species richness (species-area relationship [@lomolinoEcologyMostGeneral2000]), are buffered against disturbances [@saboRoleDischargeVariation2010], and have greater numbers of immigrant sources in the ecosystem with stable metapopulations [@takimotoEnvironmentalDeterminantsFoodchain2013]. Meanwhile, the productivity and disturbance effects are highly sensitive to the internal structure of food webs [@postProximateStructuralMechanisms2007; @takimotoEffectsProductivityDisturbance2012]. As such, the effects of disturbance and resource availability on FCL have been found to be highly variable among ecosystem types and geographic regions [@takimotoEffectsProductivityDisturbance2012; @diehlIntraguildPreySuffer2001; @takimotoEnvironmentalDeterminantsFoodchain2013; @postLongShortFoodchain2002].

@@

Under each motif, we crossed values of disturbance (frequency and intensity), productivity, and dispersal. Disturbance frequency and intensity were controlled via $p_m$ ( `r unique(df_sim$p_disturb) %>% sort()`) and $\mu_m$ (`r unique(df_sim$mean_disturb_source) %>% sort()`), respectively. Spatial disturbance patterns were regulated by variation in disturbance intensity at headwaters ($\sigma_{h}=$ `r max(df_sim$sd_disturb_source)`), and local variation ($\sigma_{l}=$ `r min(df_sim$sd_disturb_lon)`). This setup ($\sigma_h > \sigma_l$) produces high spatial variation among tributaries while allowing strong within-tributary downstream correlation [@teruiEmergentDualScaling2021], a typical pattern in real river networks [@nakamuraDisturbanceRegimesStream2000; @bendaNetworkDynamicsHypothesis2004]. We used a combination of basal species' growth rate $r_b$ and base carrying capacity $K_{base}$ (low productivity: $r_b =$ `r min(df_sim$r_b)`, $K_{base} =$ `r min(df_sim$base_k)` ; high productivity = $r_b =$ `r max(df_sim$r_b)`, $K_{base} =$ `r max(df_sim$base_k)` ) as a proxy for resource availability. For dispersal, we examined short- and long-distance dispersal scenarios (short-distance dispersal $\theta=$ `r max(df_sim$theta)`; long-distance dispersal $\theta=$ `r min(df_sim$theta)`) with constant dispersal probability ($p_{d}=$ `r unique(df_sim$p_dispersal)`). Parameter values were summarized in **Table 1**.

@@

The most significant finding in this study is the synergistic effects between ecosystem geometry and disturbance. Our no-disturbance scenario can be viewed as habitat networks having nearly homogeneous environments, in which long food chains were generally supported independently of ecosystem size and complexity (except the chain motif with low productivity). However, as the frequency of intense disturbance increases, small and/or simple networks become unable to maintain long food chains. Here, increased ecosystem size and complexity may give greater resistance to disturbance through different mechanisms. Ecosystem size increases the "total amount" of disturbance refugia, from which dispersing propagules recolonize impacted habitat patches. In the meantime, ecosystem complexity may increase the connectivity to disturbance refugia. Branching shortens the mean distance between patches and, therefore, may enhance immigration from less disturbed patches (**Figure S10**). The proportion of disturbance refugia may also have increased in more branched networks. However, we did not observe a clear proportional increase in disturbance refugia with increasing branching probability (**Figure 1B**). Collectively, each of the geometric features likely supports long food chains through distinct mechanisms, which may also explain the different patterns of state transitions (additive vs. insertion mechanisms) [@postProximateStructuralMechanisms2007]. While empirical studies rarely looked at the influence of ecosystem complexity on FCL, several studies provide some support for this theoretical prediction. For example, @sullivanEcosystemStructureEmerges2015 reported FCL is controlled primarily by the number of tributary confluences in Idaho streams. Similarly, it has been shown that the merging of major tributaries lengthened FCL in the Colorado River, especially during a post-monsoon turbid water phase [@saboPulsedFlowsTributary2018]. More empirical research is needed to confirm our theoretical predictions.

### 2023-03-09 rmd/reply1.Rmd
edit: manuscript

> Thank you for your careful review - your review improved our manuscript substantially. We followed your advise -- please see our response below.

@@

> This is a nice comment! Yes, we have clarified this point in the revised manuscript by adding a paragraph in the discussion (XXX). Also, we changed the language in Results (XXX).

@@

> Agreed. We simulated a wider range of $p_m$ values to see how disturbance frequency changes FCL-geometry relationships (please see revised figures). We also included a different level of disturbance intensity ($\mu_m = 0.2$) - the lower intensity weakened the interactive effect of disturbance frequency. We noted this result in the revised MS (XXX).

@@

@@

> Thank you for this very important comment! We have completely rewrote the model as an extension of the Nicholson-Bailey model. Important results were similar, but there were some qualitative changes as well. We have fully re-structured the Method section based on this revision.

@@

> Thank you, we have corrected this point as well.

@@

> We appreciate your insights. We revisited the switching function to properly represent this in a discrete form.

@@

> The reviewer is correct. We have address this point.

@@

> Thank you, we have revised as follows: "...theoretical conceptualization has implicitly assumed two-dimensional systems, which may be a fair approximation of lakes."

@@

> Thank you for raising this point. Ecosystem size increases the total carrying capacity, while ecosystem complexity decreases it (branching disproportionately increases the number of headwaters with low carrying capacities). Our additional analysis indicated that the "chain" motif is particularly influenced by local carrying capacity; in the meantime, omnivory scenarios were insensitive to local carrying capacity. We have clarified these points in Results and Discussion.

@@

@@

@@

> In light of comments from Reviewer 1, we have reanalyzed and fully re-structured Results and Discussion according to the new results. The above statement does not hold in the revised MS, so they have been removed.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

> Thank you for your careful review - this reviewer's comments improved our manuscript substantially. We followed your advise -- please see our response below.

@@

> This is a nice comment! Yes, we have clarified this point in the revised manuscript by adding a paragraph in Discussion (3rd paragraph). Also, we changed the language in Results.

@@

> Agreed. We simulated a wider range of $p_m$ values to see how disturbance frequency changes FCL-geometry relationships (please see revised figures). We also included a different level of disturbance intensity ($\mu_m = 0.2$) - the lower intensity removed the interactive effect of disturbance frequency. We noted this result in the revised manuscript (Results, section *Interactive effect of ecosystem geometry and disturbance*).

@@

> Thank you for your comment. We have given a deep thought on this. After the re-analysis, our interpretation is the following: ecosystem size increases the total "amount" of disturbance refuges, while branching increases the "connectivity" to refuges; branching shortens mean distance between a given pair of patches (F**igure S10**). We also looked at the proportional distribution of disturbance intensity within a network -- however, branching did not increase the proportional amount of refuges substantially (some increases in the left tail, but marginal; note we changed parameters of $\sigma_h$ and $\sigma_l$ in the revised MS). Therefore, we believe that increased connectivity, which facilitates the recolonization from less disturbed patches, was the primary mechanism that increased the resistance to disturbance.
>
> In terms of the frequency, the "disturbance intensity" refers to the proportional reduction of a population if a regional disturbance occurs (all habitat patches are affected) - therefore, the frequency does not change the relative frequency of disturbance intensity (the temporal mean of disturbance intensity at each patch is fixed). Thank you for your insights though!

@@

> Thank you for this very important comment! We have fully rewrote the model as an extension of the Nicholson-Bailey model, following Hassel 2000 and Weide et al. 2019. Important results were similar. We have fully re-structured the Method section based on this revision.

@@

> Thank you, we have corrected this point as well. We followed the guidance in Hassel 2000.

@@

> We appreciate your insights. We revisited the switching function to properly represent this in a discrete form (used a function in Hassel 2000; please see the main text).

@@

> The reviewer is correct. We have addressed this point.

@@

> Thank you, we have revised as follows: "...theoretical conceptualization has implicitly assumed two-dimensional systems, which may be a fair approximation of lakes and..."

@@

> Thank you for raising this point. Ecosystem size increases the total carrying capacity, while ecosystem complexity decreases it (branching disproportionately increases the number of headwaters with low carrying capacities; see **Figure S10**). Our additional analysis indicated that the "chain" motif is particularly influenced by local carrying capacity; in the meantime, omnivory scenarios were less sensitive to local carrying capacity. We have clarified these points in Results and Discussion.

@@

> In the revised MS, we used a combination of $r_b$ and $K_{base}$ as a proxy for productivity.

@@

> Our unclear explanation seems to cause confusion - disturbance intensity was expressed as the proportional reduction of a population. So, it ranges from 0 to 1. The vertical line is the mean disturbance intensity at headwaters. We have revised the figure legends carefully.

@@

> In light of comments from Reviewer 1, we have reanalyzed and fully re-structured Results and Discussion according to the new results. Please see our response to your next comment for details.

@@

> We agree. We have changed the figures to better visualize "state transitions" (e.g., from "B + C + P" to "B + P"). As you suggested, we did observed the exclusion of C with high productivity, but only with the weak omnivory motif. This is probably because in this motif, the contribution of B to P is sufficiently high yet maintains strong predation impact on C. We have included this statement in Results (see *Productivity effect*) and expanded the discussion.

@@

> We appreciate your insight. In the revised MS, we used a combination of $r_b$ and carrying capacity to represent low and high productivity scenarios. Indeed. it has greatly changed the results. Please see the revised results in the main text.

@@

> Agreed, it will certainly help improve the understanding of how branching affects FCL. However, we are afraid that the inclusion of this aspect is beyond the scope of this manuscript. The current manuscript contains rich amount of results, and adding a new component would make the manuscript less accessible. We appreciate your input.

@@

> True. We have removed this statement in the revised MS. Although it might be possible to quantify effect sizes and compare them, this result is not a significant portion of the manuscript.

@@

> In the re-analysis, we did observe stronger effects of productivity (see *Productivity effect* in Results). We have fully restructured it and expended discussion according to this change.

@@

> We are glad the reviewer picked it! Although the darkness was supposed to represent the strength of trophic interactions, we removed this because it might cause confusion. This figure is just a conceptual visualization and does not quantitatively represent simulation setups.

@@

> Thank you. We have reworded. Smaller/simpler ecosystems were more vulnerable to disturbance.

@@

> We have removed this part of text during the current revision.

@@

> The comment ended in the middle, so we were not able to correctly understand the meaning of this. However, we suspect the referenced sentence needs to be improved. We have fully restructured this part in the revised MS because ecosystem geometry effects were now dependent on omnivory.

@@

> Thank you, we have used another term "ecosystem geometry" (size and complexity) and clearly defined in Introduction. This eliminated the confusion between ecosystem vs. food web structure.

@@

> Corrected.

### 2023-03-09 rmd/suppl_info.Rmd
edit: manuscript

We performed one-patch simulations to identify parameter combinations that allow stable coexistence of the three species without dispersal and disturbance. Specifically, we varied attack rates $a_{ij}$, handling time $h_{ij}$, intrinsic growth rate of the basal species $r_b$, and carrying capacity $K$. First, we considered `r nrow(dplyr::distinct(df_sim1, r_b, k, a1, h))` discrete combinations of $a_{BC}$, $r_b$, $K$, and $h$ (assumed $h_{ij} = h$). We further crossed `r nrow(dplyr::distinct(df_sim1, a2))` values of $a_{BP}$ (`r min(df_sim1$a2)` -- `r max(df_sim1$a2)` with an equal interval) and $a_{CP}$ (`r min(df_sim1$a3)` -- `r max(df_sim1$a3)`), resulting in `r nrow(dplyr::distinct(df_sim1, a2, a3))` combinations. Consequently, we had a total of `r nrow(dplyr::distinct(df_sim1, r_b, k, a1, a2, a3, h))` combinations (`r nrow(dplyr::distinct(df_sim1, r_b, k, a1, h))` $\times$ `r nrow(dplyr::distinct(df_sim1, a2, a3))`) for one-patch simulations. Note that we set the switching parmeter $s = 0$ if $a_{BP} = 0$, otherwise $s = 1$. Parameter values were summarized in **Table S1**.

For each parameter combination, we ran 10 replications of `r n_sim[1]` time steps, which include `r n_sim[2]` warmup and `r n_sim[3]` burn-in periods. We recorded the patch state as numeric values ("No species" = 0, "B" = 1, "B + C" = 2, "B + P" =3, and "B + C + P" = 4) at $t = 1600$ and retrieved the maximum value of 10 replicates.

Results were summarized in **Figures S1 and S2**. We identified the following three parameter combinations that could maintain the state of "B + C + P" with distinct food web motifs: "chain (no omnivory)" $(a_{BP}, a_{CP}, h) = (0, 0.0025, 0.5)$, "weak omnivory" ($0.02, 0.025, 0.5$), and "strong omnivory" ($0.04, 0.0025, 0.75$) (see symbols in **Figures S1 and S2**). In the maintext, we reported the results with $a_{BC} = 0.5$ because qualitative patterns did not depend on $a_{BC}$.

@@

kable(df_value,
      escape = FALSE,
      booktabs = TRUE,
      caption = "Parameter values used in the main simulation and one-patch simulation") %>% 
  kableExtra::kable_styling(latex_options = 'HOLD_position')
```

@@

```{r fig1, fig.cap="Results of one-patch simulation with $a_{BC} = 0.25$. Colors indicate the patch state, and points with different symbols identify parameter combinations used in the main simulation. Panels distinguishh the value of carrying capacity $K$. In both panels, rows represent different values of intrinsic growth rate $r_b$, and columns identify handling time $h$."}
knitr::include_graphics(here::here("figure/figure_si_one_patch_a1_25.pdf"))
```

@@

```{r fig2, fig.cap="Results of one-patch simulation with $a_{BC} = 0.50$. Colors indicate the patch state, and points with different symbols identify parameter combinations used in the main simulation. Panels distinguishh the value of carrying capacity $K$. In both panels, rows represent different values of intrinsic growth rate $r_b$, and columns identify handling time $h$."}
knitr::include_graphics(here::here("figure/figure_si_one_patch_a1_50.pdf"))
```

@@

```{r fig3, fig.cap="Relationships between food chain length and ecosystem size with low disturbance intensity $\\mu_m = 0.2$. Rows distinguish food web motifs, and columns indicate different dispersal and productivity scenarios."}
knitr::include_graphics(here::here("figure/figure_si_n_patch.pdf"))
```

>>>>

We performed one-patch simulations to identify parameter combinations that allow stable coexistence of the three species without dispersal and disturbance. Specifically, we varied attack rates $a_{ij}$, handling time $h_{ij}$, intrinsic growth rate of the basal species $r_b$, and carrying capacity $K$. First, we considered `r nrow(dplyr::distinct(df_sim1, r_b, k, a1, h))` discrete combinations of $a_{BC}$, $r_b$, $K$, and $h$ (assumed $h_{ij} = h$). We further crossed `r nrow(dplyr::distinct(df_sim1, a2))` values of $a_{BP}$ (`r min(df_sim1$a2)` -- `r max(df_sim1$a2)` with an equal interval) and $a_{CP}$ (`r min(df_sim1$a3)` -- `r max(df_sim1$a3)`), resulting in `r nrow(dplyr::distinct(df_sim1, a2, a3))` combinations. Consequently, we had a total of `r nrow(dplyr::distinct(df_sim1, r_b, k, a1, a2, a3, h))` combinations (`r nrow(dplyr::distinct(df_sim1, r_b, k, a1, h))` $\times$ `r nrow(dplyr::distinct(df_sim1, a2, a3))`) for one-patch simulations. Note that we set the switching parameter $s = 0$ if $a_{BP} = 0$; otherwise $s = 1$. Parameter values were summarized in **Table S1**.

For each parameter combination, we ran ten replications of `r n_sim[1]` time steps, which include `r n_sim[2]` warmup and `r n_sim[3]` burn-in periods. We recorded the patch state as numeric values ("No species" = 0, "B" = 1, "B + C" = 2, "B + P" =3, and "B + C + P" = 4) at $t = 1600$ and retrieved the maximum value of ten replicates.

Results were summarized in **Figures S1 and S2**. We identified the following three parameter combinations that could maintain the state of "B + C + P" with distinct food web motifs: "chain (no omnivory)" $(a_{BP}, a_{CP}, h) = (0, 0.0025, 0.5)$, "weak omnivory" ($0.02, 0.025, 0.5$), and "strong omnivory" ($0.04, 0.0025, 0.75$) (see symbols in **Figures S1 and S2**). In the main text, we reported the results with $a_{BC} = 0.5$ because qualitative patterns did not depend on $a_{BC}$.

@@

kable(df_value,
      escape = FALSE,
      booktabs = TRUE,
      caption = "Parameter values used in the main and one-patch simulation") %>% 
  kableExtra::kable_styling(latex_options = 'HOLD_position')
```

@@

```{r fig1, fig.cap="Results of one-patch simulation with $a_{BC} = 0.25$. Colors indicate the patch state, and points with different symbols identify parameter combinations used in the main simulation. Panels distinguish the value of carrying capacity $K$. In both panels, rows represent different values of intrinsic growth rate $r_b$, and columns identify handling time $h$."}
knitr::include_graphics(here::here("figure/figure_si_one_patch_a1_25.pdf"))
```

@@

```{r fig2, fig.cap="Results of one-patch simulation with $a_{BC} = 0.50$. Colors indicate the patch state, and points with different symbols identify parameter combinations used in the main simulation. Panels distinguish the value of carrying capacity $K$. In both panels, rows represent different values of intrinsic growth rate $r_b$, and columns identify handling time $h$."}
knitr::include_graphics(here::here("figure/figure_si_one_patch_a1_50.pdf"))
```

@@

```{r fig3, fig.cap="Relationships between food chain length and ecosystem size with low disturbance intensity $\\mu_m = 0.2$. Lines indicate loess curves, and shades are associated 95% confidence intervals. Rows distinguish food web motifs, and columns indicate different dispersal and productivity scenarios. Different line colors indicate different disturbance probabilities."}
knitr::include_graphics(here::here("figure/figure_si_n_patch.pdf"))
```
